### 2023-04-21 paper/content.tex
Updates from Overleaf

Several branches of Earth Sciences have demonstrated the importance of the
``spatiality" of the data on a microscopic scale, mainly in geochemistry and
geochronology applications where it is possible to perform punctual analysis
and compositional maps, allowing significant advances in the understanding of
igneous, metamorphic and sedimentary processes \citep{Verberne2020, Barnes2019,
Davidson2007}. Classical paleomagnetic techniques, on the other hand, consist
in analyzing bulk samples, where the magnetic signal of a single specimen is
the result of the sum of moments of a large assembly of ferromagnetic grains
\citep{Dunlop1997}. Typically, a standard paleomagnetic sample of
approximately \qty{10}{\cm\cubed} would contain hundreds of thousands
to millions of magnetic particles with sizes varying from magnetically stable
single-domain (SD) and vortex state grains (also called pseudo-single domain,
PSD) with sizes below \qty{1}{\um}, to large ($\gg \qty{1}{\um}$) grains with
multi-domain (MD) magnetic structures, which are less stable magnetic recorders
\citep{Berndt2016}. These large MD grains usually conceal the signal of the SD
and PSD grains, and techniques of step-wise thermal and magnetic treatments are
needed to unveil the more stable and reliable magnetic record
\citep{Tauxe2018}. Recently, magnetic microscopy techniques opened the
possibility of performing magnetic maps at the micro-scale and recovering the
magnetization of each grain, therefore enabling the separate analysis of stable
and unstable magnetic particles \citep{DeGroot2018, Lima2014, Weiss2007,
DeGroot2014}.

In order to apply magnetic microscopy to paleomagnetic studies, it is necessary
to recover from the magnetic images a large amount of individual magnetic
moments, corresponding to at least tens of thousands of stable fine-grained
grains ($< \qty{1}{\um}$), in order to provide statistical significance to the
remanence vector \citep[e.g., ][]{Berndt2016}. Nowadays, with the development of
magnetic microscopy techniques, this task is no longer limited by the
resolution of magnetic microscopes \citep{Fu2020, Weiss2007, DeGroot2018,
Glenn2017, Lima2014}, but essentially by the intrinsic problem presented by the
ambiguity in the inversion of potential field data \citep{Barbosa2011,
DeGroot2021, Oliveira2015Estimation}, and ultimately by the lack of a fast and
automated way to recover such a large number of individual magnetic moments
from a set of magnetic images \citep{CortesOrtuno2022, Lima2013, Lima2009}. A
solution to the non-uniqueness of magnetic moment inversion is to add
independent prior information, such as the position of the ferromagnetic
particles \citep{Fabian2019}. This can be obtained, for example, from X-ray
computed tomography \citep[microCT; ][]{Fabian2019, DeGroot2021, DeGroot2018}.
Nonetheless, the standard microCT techniques do not provide adequate resolution
to resolve the finer and more stable magnetic grains \citep{CortesOrtuno2022,
DeGroot2021}, whereas other more sophisticated techniques such as ptychographic
X-ray tomography \citep[e.g., ][]{Maldanis2020} are not readily available and
too time-consuming to be routinely used in paleomagnetic studies.

Another route to be explored in the inversion of magnetic microscopy images is
to obtain all the information, i.e. the magnetic moment and the position of the
sources, from the magnetic data itself \citep[e.g., ][]{Fu2020}. For that, we can
explore the techniques developed in exploration geophysics, in spite of the
differences between aeromagnetic surveys and magnetic microscopy
\citep{Lima2013}. Magnetic microscopy images commonly show the combined signal
of multiple magnetic particles and can vary greatly in wavelength, strength,
and spatial separation, depending on the NRM and location of each particle. We
usually assume that the signal measured by the magnetic microscope is the
vertical component of the magnetic induction vector ($b_z$), the measurements
are performed on a regular grid with evenly spaced grid points and at a
constant height, and the data are contaminated with random Gaussian noise and
long-wavelength noise (akin to a regional signal in aeromagnetic data). Here,
we provide a methodological routine to retrieve the individual magnetic moment
of ferromagnetic grains in magnetic microscopy images following the approach
devised by \citet{Oliveira2015Estimation} for the interpretation of
aeromagnetic anomalies. The method we propose allows one to quickly and
semi-automatically estimate the individual magnetic moment vector of the stable
magnetic carriers, making use of only the magnetic images themselves and an
assumption of approximately dipolar sources. If used on a large scale, the
method provides the means to scan large areas of the rock sample, attaining
potentially the number of magnetic moments necessary for paleomagnetic studies.

@@

\noindent
and likewise for the $y$ and $z$ directions, in which $\Delta x$ is the grid
spacing (assumed to be equal in the $x$ and $y$ directions). For the $z$
component, $\Delta z = \Delta x$ and $f(x, y, z + \Delta z)$ and
$f(x, y, z - \Delta z)$ are calculated by upward and downward continuation,
respectively, performed in the wavenumber domain. The 2D maps of the $x$, $y$,
and $z$ derivatives will also be used in the Euler Deconvolution step described
below, which is known to be highly sensitive to noise in the derivatives
\citep{Saleh2012Applying}. This is why e prefer the finite-differences based
derivatives, which are less prone to amplifying short-wavelength noise than
those calculated in the wavenumber domain through the Fast Fourier Transform
(FFT).

@@

Once the locations and sizes of the windows containing the isolated signals of
each particle are determined, we can apply the Euler Deconvolution (ED)
estimate of the $x$, $y$, and $z$ positions of the center of the particles
under a dipolar approximation. This technique was first proposed by
\citet{Thompson1982} under the name EULDPH and later extended to three
dimensions and renamed ``Euler Deconvolution'' by \citet{Reid1990}. ED is
traditionally performed on a set of moving windows that scan the entire
dataset, producing a large scatter of position estimates, most of which are
spurious \citep{Silva20033D}. This is only done because it is impractical to
segment an aeromagnetic dataset into individual anomalies. Fortunately,
magnetic microscopy images contain fewer elongated features (e.g., dikes and
suture zones) and regional signals (e.g., Curie depth variations) that are
difficult to separate. This makes it possible for us to produce isolated
signals for each magnetic particle through the source detection step described
above. Since each data window contains only the signal of a single particle, we
are able to apply ED and generate only a single position estimate per particle.

@@

Parameters retrieved during inversion procedures may not always explain the observed data perfectly.
Hence, it is necessary to evaluate how well the predicted data is able to fit the observed data. 
When evaluating the goodness of fit of inversions of magnetic microscopy data, \citet{Fu2020} apply a ``non-dipolarity parameter'' ($D$). 
We note that $D$ is equivalent to the coefficient of determination

@@

The spatiality of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism.
Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution. 
Figure~\ref{complex-synthetic-comparison} shows the spatial locations of the 99 sources that were identified and the differences between the estimated dipole moments and the true values.
The depth and dipole moment amplitude of each source are represented by horizontal and vertical bars, respectively. 
These two variables are useful proxies for the strength and spatial extent of the signal of each source,
which can tell us about the limitations in strengths and sizes of the source signal that the technique is able to correctly invert.
Figure~\ref{complex-synthetic-comparison}a shows the absolute value of the angular difference between the true and the estimated dipole moment vectors. 
Figure~\ref{complex-synthetic-comparison}b shows the percentage difference between the true and estimated dipole moment magnitudes ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$). 
Figure~\ref{complex-synthetic-comparison}c shows the $R^2$ coefficient (Equation~\ref{eq_r2}), which is equivalent to the non-dipolarity parameter of \citet{Fu2020} and represents how well the dipolar model is able to explain the observed data of each source. 
Figure~\ref{complex-synthetic-comparison}d shows the SNR (Equation~\ref{eq_snr}), which expresses the power of the observed data over that of the inversion residuals.
High SNR values correspond to small inversion residuals which indicate that a dipolar model was able to explain the observed data.
Consequently, the variation of SNR values is similar to that of the $R^2$ coefficient.
Figure~\ref{complex-synthetic-comparison} shows that large errors in the estimated dipole moment direction are associated with low values of $R^2$ and SNR.
Conversely, the correlation between errors in dipole moment magnititude and $R^2$ and SNR is less pronounced, with some poor magnitude estimates being associated with $R^2$ and SNR indicating a good fit of the dipolar model.
It is also noticeable that the majority of cases where the dipole moment direction error is large are associated with deep and low-amplitude sources that are close to shallower or higher-amplitude sources.
These results indicated that $R^2$ and SNR can be used as selection criteria to discard sources with likely high errors in the estimated dipole moment.

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{real-data}a) with a grid
spacing of 2.35 $\mu$m and a sensor-sample distance of 5 $\mu$m, totaling
576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field \citep{Fu2020,
Glenn2017}. After applying the magnetic anomaly detection algorithm, it was
possible to determine the windows for 75 potential sources
(Figure~\ref{real-data}e).

@@

Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure. 
In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}. 
This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}. 
However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples. 
The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021}. 
The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}. 
Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used. 
The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}. 
The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}. 
But, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.

>>>>

Several branches of Earth Sciences have demonstrated the importance of spatial resolution on a microscopic scale. For example, geochemistry and
geochronology applications have benefited from point-wise analyses
and compositional maps, allowing significant advances in the understanding of
igneous, metamorphic and sedimentary processes \citep{Verberne2020, Barnes2019,
Davidson2007}. Classical paleomagnetic techniques, on the other hand, consist
of analyzing bulk samples, where the magnetic signal of a single specimen is
the result of the sum of moments of a large assembly of ferromagnetic grains
\citep{Dunlop1997}. Typically, a standard paleomagnetic sample of
approximately \qty{10}{\cm\cubed} would contain hundreds of thousands
to millions of magnetic particles with sizes varying from magnetically stable
single-domain (SD) and vortex state grains (also called pseudo-single domain,
PSD) with sizes below \qty{1}{\um}, to large ($\gg \qty{1}{\um}$) grains with
multi-domain (MD) magnetic structures, which are less stable magnetic recorders
\citep{Berndt2016}. These large MD grains usually conceal the signal of the SD
and PSD grains, and techniques of step-wise thermal and magnetic treatments are
needed to unveil this more stable and reliable magnetic record
\citep{Tauxe2018}. Recently, magnetic microscopy techniques opened the
possibility of obtaining magnetic field maps at the micro-scale and recovering the
magnetization of each grain, therefore enabling the separate analysis of stable
and unstable magnetic particles \citep{DeGroot2018, Lima2014, Weiss2007,
DeGroot2014}.

In order to apply magnetic microscopy to paleomagnetic studies, it is necessary
to recover from the magnetic images a large number of individual magnetic
moments, corresponding to at least tens of thousands of stable fine-grained
grains ($< \qty{1}{\um}$), in order to provide statistical significance to the
remanence vector \citep[e.g., ][]{Berndt2016}. Nowadays, with the development of
magnetic microscopy techniques, this task is no longer limited by the
resolution of magnetic microscopes \citep{Fu2020, Weiss2007, DeGroot2018,
Glenn2017, Lima2014}, but essentially by the intrinsic problem presented by the
ambiguity in the inversion of potential field data \citep{Barbosa2011,
DeGroot2021, Oliveira2015Estimation}, and ultimately by the lack of a fast and
automated way to recover such a large number of individual magnetic moments
from a set of magnetic images \citep{CortesOrtuno2022, Lima2013, Lima2009}. A
solution to the non-uniqueness of magnetic moment inversion is to add
independent prior information, such as the position of the ferromagnetic
particles \citep{Fabian2019}. This can be obtained, for example, from X-ray
computed tomography \citep[microCT; ][]{Fabian2019, DeGroot2021, DeGroot2018}.
Nonetheless, the standard microCT techniques do not provide adequate resolution
to resolve the finer and more stable magnetic grains \citep{CortesOrtuno2022,
DeGroot2021}, whereas other more sophisticated techniques such as ptychographic
X-ray tomography \citep[e.g., ][]{Maldanis2020} are not readily available and
too time-consuming to be routinely used in paleomagnetic studies.

Another route to be explored in the inversion of magnetic microscopy images is
to obtain all the information, i.e. the magnetic moment and the position of the
sources, from the magnetic data itself \citep[e.g., ][]{Fu2020}. For that, we can
explore the techniques developed in exploration geophysics, in spite of the
differences between aeromagnetic surveys and magnetic microscopy
\citep{Lima2013}. Magnetic microscopy images commonly show the combined signal
of multiple magnetic particles and can vary greatly in wavelength, strength,
and spatial separation, depending on the natural remanent magnetization (NRM) and location of each particle. We
usually assume that the signal measured by the magnetic microscope is the
vertical component of the magnetic induction vector ($b_z$), the measurements
are performed on a regular grid with evenly spaced grid points and at a
constant height, and the data are contaminated with random Gaussian noise and
long-wavelength noise (akin to a regional signal in aeromagnetic data). Here,
we provide a methodological routine to retrieve the individual magnetic moment
of ferromagnetic grains in magnetic microscopy images following the approach
devised by \citet{Oliveira2015Estimation} for the interpretation of
aeromagnetic anomalies. The method we propose allows one to quickly and
semi-automatically estimate the individual magnetic moment vector of the stable
magnetic carriers, making use of only the magnetic images themselves and an
assumption of approximately dipolar sources. If used on a large scale, the
method provides the means to scan large areas of the rock sample, attaining
potentially the number of magnetic moments necessary for paleomagnetic studies.

@@

\noindent
and likewise for the $y$ and $z$ directions, in which $\Delta x$ is the grid
spacing (assumed to be equal in the $x$ and $y$ directions). For the $z$
component, $\Delta z = \Delta x$ and $f(x, y, z + \Delta z)$ and
$f(x, y, z - \Delta z)$ are calculated by upward and downward continuation,
respectively, performed in the wavenumber domain. The 2D maps of the $x$, $y$,
and $z$ derivatives will also be used in the Euler Deconvolution step described
below, which is known to be highly sensitive to noise in the derivatives
\citep{Saleh2012Applying}. This is why we prefer the finite-differences based
derivatives, which are less prone to amplifying short-wavelength noise than
those calculated in the wavenumber domain through the Fast Fourier Transform
(FFT).

@@

Once the locations and sizes of the windows containing the isolated signals of
each particle are determined, we can apply the Euler Deconvolution (ED)
estimate of the $x$, $y$, and $z$ positions of the center of the particles
under a dipolar approximation. This technique was first proposed by
\citet{Thompson1982} under the name EULDPH and later extended to three
dimensions and renamed ``Euler Deconvolution'' by \citet{Reid1990}. ED is
traditionally performed on a set of moving windows that scan the entire
dataset, producing a large scatter of position estimates, most of which are
spurious \citep{Silva20033D}. This is only done because it is impractical to
segment an aeromagnetic dataset into individual anomalies. Fortunately,
magnetic microscopy images often contain fewer elongated features (e.g., dikes and
suture zones) and regional signals (e.g., Curie depth variations) that are
difficult to separate. This makes it possible for us to produce isolated
signals for each magnetic particle through the source detection step described
above. Since each data window contains only the signal of a single particle, we
are able to apply ED and generate only a single position estimate per particle.

@@

Parameters retrieved during inversion procedures may not always explain the observed data perfectly.
Hence, it is necessary to evaluate how well the predicted data is able to fit the observed data. 
When evaluating the goodness of fit of inversions of magnetic microscopy data, \citet{Fu2020} apply a ``dipolarity parameter'' ($D$). 
We note that $D$ is equivalent to the coefficient of determination

@@

The spatial resolution of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism.
Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution. 
Figure~\ref{complex-synthetic-comparison} shows the spatial locations of the 99 sources that were identified and the differences between the estimated dipole moments and the true values.
The depth and dipole moment amplitude of each source are represented by horizontal and vertical bars, respectively. 
These two variables are useful proxies for the strength and spatial extent of the signal of each source,
which can tell us about the limitations in strengths and sizes of the source signal that the technique is able to correctly invert.
Figure~\ref{complex-synthetic-comparison}a shows the absolute value of the angular difference between the true and the estimated dipole moment vectors. 
Figure~\ref{complex-synthetic-comparison}b shows the percentage difference between the true and estimated dipole moment magnitudes ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$). 
Figure~\ref{complex-synthetic-comparison}c shows the $R^2$ coefficient (Equation~\ref{eq_r2}), which is equivalent to the non-dipolarity parameter of \citet{Fu2020} and represents how well the dipolar model is able to explain the observed data of each source. 
Figure~\ref{complex-synthetic-comparison}d shows the SNR (Equation~\ref{eq_snr}), which expresses the power of the observed data over that of the inversion residuals.
High SNR values correspond to small inversion residuals which indicate that a dipolar model was able to explain the observed data.
Consequently, the variation of SNR values is similar to that of the $R^2$ coefficient.
Figure~\ref{complex-synthetic-comparison} shows that large errors in the estimated dipole moment direction are associated with low values of $R^2$ and SNR.
Conversely, the correlation between errors in dipole moment magnititude and $R^2$ and SNR is less pronounced, with some poor magnitude estimates being associated with $R^2$ and SNR indicating a good fit of the dipolar model.
It is also noticeable that the majority of cases where the dipole moment direction error is large are associated with deep and low-amplitude sources that are close to shallower or higher-amplitude sources.
These results indicated that $R^2$ and SNR can be used as selection criteria to discard sources with likely high errors in the estimated dipole moment.

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately 1410 $\mu$m x 2256 $\mu$m (Figure~\ref{real-data}a) with a grid
spacing of 2.35 $\mu$m and a sensor-sample distance of approximatly 5 $\mu$m, totaling
576x10\textsuperscript{3} data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field while the data was taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($B_{z}$) using a spectral approach \citep{Fu2020,
Glenn2017}. We applied a bias field of 0.9 mT during the measurement, which was periodically reversed to result in an effective background field of <1 µT.  After applying the magnetic anomaly detection algorithm, it was
possible to determine the windows for 75 potential sources
(Figure~\ref{real-data}e).

@@

Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure. 
In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}. 
This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}. 
However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples. 
The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021}. 
The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}. 
Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used. 
The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}. 
The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}. 
In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.
